A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-02-04 report_clean/numerics.tex
cosmetic changes

\FloatBarrier
\paragraph{Condition Number}
In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
on $\nu$, for several values of $h$.
\begin{figure}
\begin{tabular}{cc}
\includegraphics[height=0.3\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
 \includegraphics[height=0.3\textwidth]{pics_frequency_domain/ey_resonance.pdf}
 \end{tabular}
 \caption{
 The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
 number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
 The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
 with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
 while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
 computed for $\nu=0$ are almost indistinguishable.}
 \label{fig:small_nu}
\end{figure}
%\begin{table}[ht!]
%\begin{tabular}{c|ccccccccc}
%\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
% \hline
%1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
%\hline
%0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
%\hline
% 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
% \hline
%0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
%\hline
% 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
%\end{tabular}
%\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
%\label{tab:cond_number}
%\end{table}
Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}.

>>>>

\FloatBarrier
\paragraph{Condition Number}
In Figure \ref{fig:small_nu} we demonstrate the dependence of the condition number of the matrix of the system (\ref{eq:simple_system}) 
on $\nu$, for several values of $h$.
\begin{figure}
\begin{tabular}{cc}
\includegraphics[height=0.35\textwidth]{pics_frequency_domain/fig_cond_num.pdf}&
 \includegraphics[height=0.35\textwidth]{pics_frequency_domain/ey_resonance.pdf}
 \end{tabular}
 \caption{
 The left plot demonstrates the dependence of the condition number of the system (\ref{eq:simple_system}) on $\nu$, for different values of $h$ (the condition 
 number for $\nu=0$ is not shown, however, for all values of $h$ as shown in the plot, the matrix was non-singular even for $\nu=0$). 
 The right plot shows $E_{y}^{\nu}$ computed on different meshes for small $\nu$. It can be seen that for meshes that are coarse 
 with respect to $\nu$ (e.g. $\nu=10^{-4}, \; h=10^{-2}$, or $\nu=0,\; h=10^{-2}$), the computed solution seems to be only piecewise-continuous in $\nu$, 
 while for finer meshes and $\nu>0$ the solution seems to be smooth. It can be also seen that for $h=10^{-2}$ and $h=10^{-3}$ the solutions 
 computed for $\nu=0$ are almost indistinguishable.}
 \label{fig:small_nu}
\end{figure}
%\begin{table}[ht!]
%\begin{tabular}{c|ccccccccc}
%\diagbox[width=10em]{$h$}{$\nu$}& 100 & 10 & 1 & 0.1 & 1e-2 & 1e-3 & 1e-4 & 1e-8 & 0\\
% \hline
%1 & 3.9634&4.3787 &4.987&36.949&42.394& 42.757 &42.79&42.793&42.793\\
%\hline
%0.5&      3.9931& 6.87&48.473 & 168.41  &207.34  & 209.63 & 209.83 & 209.85&  209.85\\
%\hline
% 0.1&      16.09  &     159.56  &     1146.1   &    8304.1   &     19169  &      20270   &     20344   &     20352   &     20352\\
% \hline
%0.05&      64.046  &     637.18  &     4686.2   &     38876 &  1.4e5 &  1.58e5 &   1.58e5 &  1.58e5 &  1.58e5\\
%\hline
% 0.01&       1600    &   15921 & 1.2e5  & 1.1e6 & 8.3e6  & 1.8e7   & 1.93e7  & 1.93e7  & 1.93e7\\
%\end{tabular}
%\caption{The condition number of the matrix of the system (\ref{eq:simple_system}) for different values of $\nu$ and $h$. }
%\label{tab:cond_number}
%\end{table}
Remarkably, for $\nu=0$ the computed matrices are not singular. We do not know the exact reason for this.
As an additional illustration, we compare the solutions for very small $\nu$ and $\nu=0$ for different meshes in Fig.~\ref{fig:small_nu}.
